Примеры данных

### 2023-01-15 example_data_rus.Rmd
fix example data frontend

---
title: "Примеры данных"
author: "Антон Смирнов"
date: "2023-01-15"
output: 
  html_document:
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: false
    mathjax: "http://cdn.mathjax.org/mathjax/latest/MathJax.js?config=TeX-AMS-MML_HTMLorMML"
runtime: shiny
---

>>>>

---
title: "Примеры данных"
author: "Антон Смирнов"
date: "2023-01-15"
output: html_document
ntime: shiny
---
